Efficiently stable presentations from error-correcting codes

### 2023-10-16 efficient_stability.tex
open problems

\begin{theorem*}[Main, informal]
For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations. 
\end{theorem*}

@@

\tnote{more? open questions?}\mnote{If we have open problems, maybe we should collect them at the end? Not sure about that. Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}\tnote{There's the obvious open problem of finding an LTC that is not stable (since I'd conjecture it this way), and conversely other examples of codes that are stable. We can also ask how far things can be pushed; in principle we could have stability, in our sense, for a finite pres of an infinite group.}\mnote{Agree about most of the problems you suggested. Regarding the infinite case, there are many stability results for infinite groups... We should be precise in what we mean by efficient in the infinite case. Maybe there is a way of formulating it. Actually, I do not know of any group which is infinite, not free or a product of a free and a finite group, which has linear stability rate...}

>>>>

\begin{theorem*}[Main, informal]\label{thm:main-inf}
For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations. 
\end{theorem*}

@@

\paragraph{Open questions.}\tnote{added this paragraph}
We leave many questions open. A natural direction is to determine if there are simple sufficient conditions on the matrix $h$ that guarantee that the presentation $G(h)$ is stable. As we discussed, the condition that $\ker h$ is a testable code is equivalent to stability for $1$-dimensional permutations. It thus seems likely that testability is not a sufficient condition in general; can testability be determined by a combinatorial parameter of $h$? More generally, finding other examples of efficient stability seems of intrinsic interest, besides potential applications to property testing and the construction of nonlocal games. In a different direction, an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups, as is discussed in more depth in the work~\cite{}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}
